\begin{center}
\section*{\textbf{\Large \MakeUppercase{\textrm{Abstract}}}}
\end{center}



\begin{justify}
This thesis is for creating a web-based ER modeller and the right tool for fast-prototyping based development for websites at first.

The most of the web-pages share common properties that make them possible to be generated with just a little information. By this idea, the software introduced in this thesis is a code generator, which uses a modified entity-relationship model for the definition of generable resources. For this model, the application provides a designer interface in order to ease the use of the generator.

Respecting the readability the templates had been organized into packages. In packages, requirement files can be found, which shows, which requirements are suitable for the template package. All requirements are optional, so it gives the ability to skip unnecessary functionalities from the new system. In order to convince the users, the generator supports adding own template packages and modifying the existing ones.

So far, the code generators share a common disadvantage: The abstract definition can not be changed without re-generating the entire code. The software introduced in the thesis does not make it different but shows a solution using the Git version control system. 

By the help of this application, opportunities open up for generating not just simple but complex server- and client side codes, with opening gates to the well-structured, easily modifiable web applications. 
\end{justify}



\vspace{2cm}

{\bf Keywords:} {\it  scaffolding, web, code, generator, rapid-prototyping, ER, modeller}